\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1


\newcommand{\resumeItem}[1]{
  \item\small{
    #1 \vspace{-2pt}
  }
}
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\projectSubheading}[2]{
    \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}
\newcommand{\skillItem}[2]{
    \item[] {\textbf{#1}: #2}
}

\renewcommand{\labelitemii}{$\circ$}


\begin{document}

% HEADING %
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\LARGE Shane Williams} & \href{https://www.linkedin.com/in/shanetwilliams/}{linkedin.com/in/shanetwilliams} \\
  \href{mailto:shanethomaswilliams@gmail.com}{shanethomaswilliams@gmail.com} & \href{http://github.com/shanetwilliams/}{github.com/shanetwilliams} \\
\end{tabular*}


% EDUCATION %
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
        {Memorial University of Newfoundland}{St. John's, Canada}
        {Bachelor of Computer Engineering; 4.00 GPA / 94.8\%; Valedictorian.}{2019 -- 2024}
\resumeSubHeadingListEnd


% EXPERIENCE %
\section{Experience}
\resumeSubHeadingListStart

    \vspace{0.5pt}

    \resumeSubheading
        {Tesla}{Palo Alto, CA}
        {Firmware Platforms Engineer}{Fall 2024 -- Present}

    \vspace{0.5pt}

    \resumeSubSubheading
        {Firmware Platforms Intern}{Fall 2023}


    \resumeItemListStart
    \resumeItem{Developing low-level drivers for numerous microcontroller families for use across the Tesla vehicle firmware org.}
    \resumeItem{Owning the firmware build system for 50+ developers, including a fresh rewrite to improve build speed by 5-20x.}
    \resumeItem{Bringing up new PCBA designs on a monthly basis, working with HW engineers on review and validation.}
    \resumeItem{Creating and maintaining internal tooling to improve embedded developer experience and efficiency.}
    \resumeItem{Creating hardware-in-the-loop testing systems for validating low-level firmware.}
    \resumeItemListEnd

    \resumeSubSubheading
        {Firmware Integration Intern}{Summer 2022}

    \resumeItemListStart
        \resumeItem{Owned several firmware features end-to-end, working with external suppliers and mechanical, electrical, firmware, regulatory and safety teams across Tesla to bring them into production.}
        \resumeItem{Wrote safety-critical vehicle firmware in bare-metal C on Cortex-M microcontrollers for interior vehicle endpoints.}
        \resumeItem{Presented prototype vehicle features to company executives.}
    \resumeItemListEnd

    \resumeSubheading
        {NVIDIA}{Santa Clara, CA}
        {Firmware Development Intern}{Fall 2021}
    \resumeItemListStart
        \resumeItem{Wrote U-Boot and embedded Linux firmware for an ARM Cortex-A processor on a custom PCIe device.}
        \resumeItem{Developed kernel and userspace drivers in C for a PCIe controller and PHY.}
    \resumeItemListEnd

    \resumeSubheading
        {Kepler Communications}{Toronto, Canada}
        {Firmware Development Intern}{Summer 2020, Winter 2021}

    \resumeItemListStart
        \resumeItem{Owned firmware development for a new cutting-edge satellite radio using C bare-metal on a Cortex-M MCU.}
        \resumeItem{Wrote satellite flight computer firmware using C and FreeRTOS on a Cortex-R processor in a Xilinx SOC.}
        \resumeItem{Wrote a satellite file system and ARQ protocol using C++ on a Linux platform, improving throughput by 5-200\%.}
    \resumeItemListEnd

\resumeSubHeadingListEnd


% PROJECTS %
\section{Projects}
\resumeSubHeadingListStart

    \projectSubheading
        {Senior Capstone Project -- Remotely Operated Quadcopter}{2023 -- 2024}
    \resumeItemListStart
        \resumeItem{Designed one of two onboard drone PCBs, including an RP2040 microcontroller, Semtech LoRa radio, USB-PD sink, power regulation, GPS, video transmitter, and a Qi wireless charging sink.}
        \resumeItem{Wrote all onboard firmware including motor controls and power management using C and FreeRTOS.}
        \resumeItem{Created tooling in Python for generating peripheral drivers for the 10+ onboard ICs from YAML register maps.}
        \resumeItem{Wrote ground station software and a control terminal program using Python and React with gRPC.}
    \resumeItemListEnd

    \projectSubheading
        {Student Team -- Killick-1 Cubesat}{2020 -- 2022}
    \resumeItemListStart
        \resumeItem{Designed the software architecture for a nanosatellite ground station and led a team of four in its implementation.}
        \resumeItem{Wrote Python for satellite tracking and communication, telemetry management, and remote control.}
    \resumeItemListEnd

    \projectSubheading
        {shanewilliams.ca}{2024 -- Present}
    \resumeItemListStart
        \resumeItem{A personal website written in Svelte and Python dedicated to Canadian political data visualization.}
    \resumeItemListEnd

\resumeSubHeadingListEnd


% SKILLS %
\section{Skills}
\resumeSubHeadingListStart

    \vspace{6pt}
    \setlength\itemsep{0px}
    \skillItem{Languages}{C, C++, Python, Java, Rust, Javascript}
    \skillItem{Tools \& Frameworks}{Linux, U-Boot, FreeRTOS, Make, CMake, SCons, Buck2, GDB, Git, Docker, OpenGL}
    \skillItem{Protocols}{HDMI, PCIe, TCP, UDP, SPI, I2C, I2S, UART, CAN, LIN, LoRa}
    \skillItem{Hardware}{PCB schematic \& layout with KiCAD; LV system design; PCB bringup, rework, and lab skills }

    \resumeSubHeadingListEnd

\end{document}
